Argennon: A Scalable Smart Contract Platform

### 2021-07-13 tex/sections/elements.tex
Add RESTful properties to README.md
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

\begin{lstlisting}[language=python, frame=TB, float, title=An Argennon transaction in YAML format,label={lst:txn-example}]
---
fee: |
    PUT /balances/0x73.0xa2?to=fee&amount=0.26&sig=5b73CbmwQNRC7fWUY15 HTTP/1.1
call: |
    POST httpb://bac.argennon.net/54.189.21/proposals HTTP/1.1
    Content-Type: application/json; charset=utf-8
    Content-Length: 69

>>>>

\begin{lstlisting}[language=python, frame=TB, float, title=An Argennon transaction in YAML format,label={lst:txn-example}]
---
fee: |
    PUT /balances/0x73.0xa2?to=fee&amount=0.26&sig=5b73CbmwQNRC7fWUY15 HTTP/1.1
call: |
    POST bttp://bac.argennon.net/54.189.21/proposals HTTP/1.1
    Content-Type: application/json; charset=utf-8
    Content-Length: 69
